\documentclass[10pt]{article}

%%% These are some packages that are useful
\usepackage{amsmath,amssymb, amscd,amsbsy, amsthm, enumerate}
\usepackage[export]{adjustbox}
\usepackage{lastpage}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[unicode]{hyperref}
\usepackage{tikz, pgfplots, xcolor, fancyhdr}
\usepackage{multicol}
\usepackage{lipsum}

%%% Page formatting
%\setlength{\headsep}{30pt}
\setlength{\textheight}{9in}
\newcommand{\tab}{\hspace{1cm}}
%\setlength{\parindent}{25pt}

\title{Potato Pages Review Form}
\author{Reviewer Name$^{1,2}$\\ \scriptsize{1. First Affiliation} \\ \scriptsize{2. Second Affiliation}}
\date{}

%%% Header and Footer Info
\pagestyle{fancy}
\fancyhead[L]{Potato Pages - Review Form.}
\fancyhead[C]{}
\fancyhead[R]{\date{\today}}


%\fancyhf{} % sets both header and footer to nothing
%\renewcommand{\headrulewidth}{0pt}
% your new footer definitions here

\fancyfoot[L]{}
\fancyfoot[C]{}
\fancyfoot[R]{\thepage\ of \pageref{LastPage}}

% Used to define spacing and format of References
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
	\OLDthebibliography{#1}
	\setlength{\parskip}{0pt}
	\setlength{\itemsep}{0pt plus 0.3ex}
}

%%% Document Starts now
\begin{document}

\maketitle
\thispagestyle{fancy}

Please thoroughly review the submitted article, answer the following questions and record any corrections or suggestions to the author.

\begin{enumerate}
	\item Does the article begin with the statement "consider a potato?"
	\item Please clearly select one of the following regarding publication status for the reviewed article:
	\begin{enumerate}
		\item Accept as is.
		\begin{itemize}
			\item The article has no found errors.
			\item The article is clear and concise throughout.
			\item The article has a clear purpose and meaningful conclusion.
		\end{itemize}
		\item Accept with minor revisions.
		\begin{itemize}
			\item Meaning the article has minor spelling, typos or grammatical errors.
			\item The article is clear throughout.
			\item The article has a clear purpose and conclusion.
		\end{itemize}
		\item Accept with major revisions.
		\begin{itemize}
			\item Meaning there are many mistakes that need addressed with the article.
			\item The article is not clear.
			\item The article conclusion is not clear or meaningful.
		\end{itemize}
		\item Reject with resubmission needed after major revisions/reanalysis.
		\begin{itemize}
			\item There are clear errors with the logic, analysis, or arguments in the paper.
			\item The article has no clear purpose.
			\item There is no meaningful purpose to the conclusion of the article.
		\end{itemize}
	\end{enumerate}
	\item Please provide clear and concise feedback for revisions and issues with the submitted article. These should be listed and attached to this page or submitted as corrections to the original article pdf.
	\item Should this article be considered for the Cachet Honors and Innovation Prize (CHIP)? The Potato CHIP is an award given to an individual or team of individuals based on their Potato Page submission. The award signifies a submission of superior quality.
	\item Please send completed review to thepotatopages@gmail.com within the allotted time period assigned upon receiving the original article.
\end{enumerate}




\begin{thebibliography}{9}
	{\footnotesize
	\bibitem{reff} LastName, FirstInitial. "Article Title." Potato Page Submission. Submitted on MM/DD/YYYY. Reviewed on MM/DD/YYYY.
	}
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}





















